### 2022-04-26 README.Rmd
Update readme with figures in right place

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
library(sf)
```

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  out.width = "100%"
)
```
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(sf)
```
